Future Virtual Particle Method for Pedestrian Navigation

### 2014-12-04 doc/informe/paper.tex
me olvide subir la ultima foto de pictures.pptx arreglo errores menores en el paper.tex. actualizo pdf.

Here there are two terms in the $sum$. The first term represents
the fact that $i$ does not want to be in the same location as $j$
in the near future. Note that $j'$ represents the predicted location
of $j$ inferred by another pedestrian (in this case, $i$) and because
of this, it moves it's near future away of that predicted location.
The seocond term, represents the same fact but taking in mind the
current location of the pedestrian $j$. The same law applies to each
of the walls on the simulation, the difference is that the closest
point on the wall and and the future has to be calculated before applying
the formula. Also, the constants $\alpha_{fw}$ and $\beta_{fw}$
have different values.

@@

Then, the desire force that pedestrian $i$ will aply to his future
is calculated. This force is modelled using two springs. The first
spring hast its origin attached on $i$ and its end attached on $i'$
and has a spring constant $K_{1}$. This spring will regulate the
velocity that will be calculated on a previous step at witch the pedestrian
$i$ will advance. The second spring, has its origin on $i'$ and
the end attached to the closest point on the pedestrian target area
and has a spring constant $K_{2}$. In order to avoid an oscilatory
movement (in example, with a single pedestrian), a damping $\gamma$
was added to this second spring. This spring represents how much te
pedestrian wants to reach his target. A larger spring constant will
force a more straight path, but possible with more collitions on its
way.

>>>>

Here there are two terms in the $sum$. The first term represents
the fact that $i$ does not want to be in the same location as $j$
in the near future. Note that $j'$ represents the predicted location
of $j$ inferred by another pedestrian (in this case, $i$) and because
of this, it moves it's near future away of that predicted location.
The second term, represents the same fact but taking in mind the current
location of the pedestrian $j$. The same law applies to each of the
walls on the simulation, the difference is that the closest point
on the wall and and the future has to be calculated before applying
the formula. Also, the constants $\alpha_{fw}$ and $\beta_{fw}$
have different values.

Figure 2.2 shows the external forces that a pedestrian $i$ suffers
because of another pedestrian ($j$) and also the direction in wich
$i$ desires to move.

@@

Then, the desire force that pedestrian $i$ will apply to his future
is calculated. This force is modeled using two springs. The first
spring has its origin attached on $i$ and its end attached on $i'$
with a spring constant $K_{1}$. This spring will regulate the velocity
that will be calculated on a posterior step at witch the pedestrian
$i$ will advance. The second spring, has its origin on $i'$ and
the end attached to $objective_{i}$ and has a spring constant $K_{2}$.
In order to avoid an oscilatory movement (in example, with a single
pedestrian), a damping $\gamma$ was added to this second spring.
This spring represents how much te pedestrian wants to reach his target.
A larger spring constant will force a more straight path, but possible
with more collitions on its way.
